---
title: "Taxonomomy Validation Visualizations, Comparing systems"
author: "Joe Skufca"
date:  "2022-05-17"
output: html_notebook
---

Preliminar visualiations of taxonomy usage attempts by the team to work towards validating the vehicle, analyzing *EPA Smart Growth Assessment.*

## Setup

```{r}
library(tidyverse)
library(janitor)
library(here)
library(plotly)
library(readxl)
library(heatmaply)
library("dendextend")
```

## Load data

First usage of template performed by the group is aggregated into a single excel file, with each individual rater using the template, with their ratings recorded on a different sheet in an excel file.  Processing will be identical for each file (SHPS System) under consideration.

Currently, we are considering 3 systems - EPA Smart Growth, Climate Smart Communities, and LEED for Communities.


```{r}
filelist=list(epa=here("data","taxonomy_epa_sga.xlsx"),
              csc=here("data","taxonomy_csc.xlsx"),
              lfc= here("data","20220119 SHPS Taxonomy - Template & Scoring - All In.xlsx"))
```

We construct a helper functions to read each file:

```{r}

read_sheet=function(filename,this_person){
df1=suppressMessages(read_excel(filename,sheet=this_person, 
               range = "C9:I28",col_names = FALSE)) %>%
     select(1,3,4,6,7) %>% 
     rename(dimension=...1,
            response=...3,
            resp_indicator=...4,
            degree_best=...6,
            degree_indicator=...7) %>% drop_na(dimension) %>%
     mutate(rater=this_person) 
}


read_shps_tax=function(filename){
     sheets=excel_sheets(filename)
     shps_name=names(filename)
     
          df2=map_dfr(sheets[c(1:2,4,5,6)],~ read_sheet(filename,.x)) %>%
     mutate(response=factor(response,
                            levels = c("No","Yes - Could/Should","Yes - Must/Required")),
            shps=shps_name)
     
}

df2=(read_shps_tax(unlist(filelist[1])))

dfC=map_dfr(filelist,read_shps_tax,.id="shps") %>% filter(rater!="Joe")


dfC2= dfC %>% group_by(shps) %>% nest()
```




```{r}
df3=df2 %>% select(dimension,rater,degree_best) %>%
     pivot_wider(names_from = rater,values_from = degree_best)



df3_2=dfC %>% select(shps,dimension,rater,response,degree_best) %>%
     pivot_wider(names_from = rater,values_from = c(response,degree_best))
```

```{r}

df3 %>%  
     heatmaply::heatmaply(labRow=.$dimension,
                                      main = "EPA Smart Growth, Degree of Best PracticsS")
```

```{r}


df2 %>% select(dimension,rater,response) %>% 
     mutate(response=as.numeric(response)) %>%
     pivot_wider(names_from = rater,values_from = response) %>%
     select(-dimension) %>% heatmaply(x=.,labRow=df3$dimension,
                                      main = "EPA Smart Growth, Response")
```
### histogram clusters with extend
```{r}
epa.dist=df3_2 %>% filter(shps=="epa")%>%   column_to_rownames("dimension") %>%
     select(where(is.numeric)) %>% dist()

lfc.dist=df3_2 %>% filter(shps=="lfc")%>% column_to_rownames("dimension") %>%
     select(where(is.numeric)) %>% dist()

csc.dist=df3_2 %>% filter(shps=="csc")%>% column_to_rownames("dimension") %>%
     select(where(is.numeric)) %>% dist()
```

```{r}
epa.hc=hclust(epa.dist)
lfc.hc=hclust(lfc.dist)
csc.hc=hclust(csc.dist)
```

```{r}
epa=epa.hc %>% as.dendrogram()
lfc=lfc.hc %>% as.dendrogram()
csc=csc.hc %>% as.dendrogram()
```

```{r}
dendlist(lfc, csc,epa) %>%
  untangle(method = "step2side") %>% # Find the best alignment layout
  tanglegram()                       # Draw the two dendrograms
```

