---
title: "Taxonomomy Validation Visualizations"
author: "Joe Skufca"
date:  "2022-01-26"
output: html_notebook
---

Preliminar visualiations of taxonomy usage attempts by the team to work towards validating the vehicle, analyzing Lead for Commutities.

## Setup

```{r}
library(tidyverse)
library(janitor)
library(here)
library(plotly)
library(readxl)
```

## Load data

First usage of template performed by the group is aggregated into a single excel file, with each individual rater using the template, with their ratings recorded on a different sheet in an excel file.

```{r}
filename=here("data","20220119 SHPS Taxonomy - Template & Scoring - All In.xlsx")
```

The file is quite complicated.  Let's understand that file.

```{r}
sheets=excel_sheets(filename)
```

Let's try to read a particular sheet correctly:

```{r}
this_person=sheets[1]
read_sheet=function(this_person){
df1=read_excel(filename,sheet=this_person, 
               range = "C9:I28",col_names = FALSE) %>%
     select(1,3,4,6,7) %>% 
     rename(dimension=...1,
            response=...3,
            resp_indicator=...4,
            degree_best=...6,
            degree_indicator=...7) %>% drop_na(dimension) %>%
     mutate(rater=this_person) 
}

df2=map_dfr(sheets[c(1:2,4,5,6)],read_sheet) %>%
     mutate(response=factor(response,
                            levels = c("No","Yes - Could/Should","Yes - Must/Required")))



```

```{r}
df2 %>% ggplot(aes(x=rater,y=dimension,fill=degree_best))+geom_tile()
```

```{r}
df3=df2 %>% select(dimension,rater,degree_best) %>%
     pivot_wider(names_from = rater,values_from = degree_best)
```

```{r}
library(heatmaply)
df3 %>% select(-dimension) %>% heatmaply::heatmaply(labRow=df3$dimension,
                                      main = "LEED for Community, Degree of Best Practices")
```

```{r}
df4=df2 %>% select(dimension,rater,response) %>%
     pivot_wider(names_from = rater,values_from = response)

df2 %>% select(dimension,rater,response) %>% 
     mutate(response=as.numeric(response)) %>%
     pivot_wider(names_from = rater,values_from = response) %>%
     select(-dimension) %>% heatmaply(labRow=df3$dimension,
                                      main = "Leed for Community, Response")
```


